---
title: "Assignment 1"
output: html_notebook
---

## Assignment 1

**Install R on your own machine.** 
We are Arch Linux users, so we can install these two packages:

+ [R](https://www.archlinux.org/packages/?name=r)
+ [rstudio-desktop-bin](https://aur.archlinux.org/packages/rstudio-desktop-bin)

## Assignment 2

**What is an `.r` file?**

An `.r` file is a file with R code that can be run. 

**What is an `.rmd` file?**

An `.rmd` file is a file that stores a markdown notebook that can contain R code.

## Assignment 3

**Use the help function to get insights in the following functions.**

### sample
```
help(sample)
```
```
sample takes a sample of the specified size from the elements of x using either with or without replacement.
```

### replicate
```
help(replicate)
```
```
lapply returns a list of the same length as X, each element of which is the result of applying FUN to the corresponding element of X.

sapply is a user-friendly version and wrapper of lapply by default returning a vector, matrix or, if simplify = "array", an array if appropriate, by applying simplify2array(). sapply(x, f, simplify = FALSE, USE.NAMES = FALSE) is the same as lapply(x, f).

vapply is similar to sapply, but has a pre-specified type of return value, so it can be safer (and sometimes faster) to use.

replicate is a wrapper for the common use of sapply for repeated evaluation of an expression (which will usually involve random number generation).

simplify2array() is the utility called from sapply() when simplify is not false and is similarly called from mapply().
```

### plot
```
help(plot)
```
```
Generic function for plotting of R objects. For more details about the graphical parameter arguments, see par.

For simple scatter plots, plot.default will be used. However, there are plot methods for many R objects, including functions, data.frames, density objects, etc. Use methods(plot) and the documentation for these.
```

### barplot
```
help(barplot)
```
```
Creates a bar plot with vertical or horizontal bars.
```

### table
```
help(table)
```
```
table uses the cross-classifying factors to build a contingency table of the counts at each combination of factor levels.
```

## Assignment 4

**We take take a fair dice and roll it 1000 times. Write an R program that:**

+ **simulates throwing 1000 times with a dice**
+ **shows in a graph how many times 1, 2, 3, 4, 5 and 6 have been thrown**

```{r}
library(tidyverse)

dice = seq(1, 6)
barplot(table(sample(dice, 10000, replace = T)))
```

## Assignment 5

**We throw once with three fair dices and calculate the sum of these. Make a frequency polygon that shows this experiment:**

We generate a function that can do our job because we are lazy.

```{r}
dice = seq(1, 6)
sum <- function() {
  sample(dice, 1) + sample(dice, 1) + sample(dice, 1)
}
generate_plot <- function(n) {
  barplot(table(replicate(n, sum(), simplify = T)))
}
```

### 10 times

```{r}
generate_plot(10)
```

### 100 times

```{r}
generate_plot(100)
```

### 1000 times

```{r}
generate_plot(1000)
```

### 10000 times

```{r}
generate_plot(10000)
```
