---
  title: "Assignment 2"
  output:
  html_document:
    df_print: paged
---

-----

Niek van Leeuwen en Robin Martijn

## Assignment 1

*The chance that in a box of 25 products, none are defect:*

```{r}
dbinom(0,25,0.04)
```

The chance that between 1 and 5 products are defect

```{r}
pbinom(5,25,0.04) - pbinom(1,25,0.04)
```

Dit is niet goed

```{r}
hist(rbinom(10000, 25, 0.04), breaks=50, col='lightblue')
```


## Assignment 2

*The chance that all 100 drivers are sober.*

```{r}
pbinom(0, 100, 0.014)
```
```{r}
(1-0.014)^100
```

*The chance that at least 5 percent of the drivers has consumed too much alcohol to drive.*

```{r}
1 - pbinom(4, 100, 0.014)
```

*The chance that more than half of the cyclists are not sober.*

```{r}
1 - pbinom(4, 8, 0.42)
```

## Assignment 3

*How many executions did take place in the year 2017 in the United States?*

> Of the 23 prisoners executed in 2017, a total of 16 (more than two-thirds) had been sentenced in 1999 or ealier.

[Source](https://www.bjs.gov/index.cfm?ty=pbdetail&iid=6586) 

*Calculate the chance that no innocent people were executed in 2017.*

```{r}
dbinom(0, 23, 0.04)
```

