---
  title: "Assignment 2"
  output:
  html_document:
    df_print: paged
---

-----

Niek van Leeuwen en Robin Martijn

## Assignment 1

*The chance that in a box of 25 products, none are defect:*

```{r}
dbinom(0,25,0.04)
```

*The chance that between 1 and 5 products are defect*

```{r}
pbinom(5,25,0.04) - pbinom(1,25,0.04)
```

*A graph of the probability distribution function based on simulation*

```{r}
plot(type="b", table(rbinom(100000, 25, 0.04)))
```

*A graph of the probability distribution function based on built in R functions*

```{r}
x = seq(0, 25)
plot(type = "b", dbinom(x, 25, 0.04), xlim = c(0, 8))
```


## Assignment 2

*The chance that all 100 drivers are sober.*

```{r}
pbinom(0, 100, 0.014)
```
```{r}
(1-0.014)^100
```

*The chance that at least 5 percent of the drivers has consumed too much alcohol to drive.*

```{r}
1 - pbinom(4, 100, 0.014)
```

*The chance that more than half of the cyclists are not sober.*

```{r}
1 - pbinom(4, 8, 0.42)
```

## Assignment 3

*How many executions did take place in the year 2017 in the United States?*

> Of the 23 prisoners executed in 2017, a total of 16 (more than two-thirds) had been sentenced in 1999 or ealier.

[Source](https://www.bjs.gov/index.cfm?ty=pbdetail&iid=6586) 

*Calculate the chance that no innocent people were executed in 2017.*

```{r}
dbinom(0, 23, 0.04)
```

## Assignment 4

*A reporting centre receives 15 reports per day. Calculate:*

+ *The chance that between 0.00 and 08.00 no reports come in*

```{r}
dpois(0, 15/3)
```

+ *The chance of there being at least three hours and a maximum of six hours between two reports.*

```{r}
pexp(6, 15/24) - pexp(3, 15/24)
```

*Create a graph that compares the chance of not getting a report with the elapsed time.*

```{r}
plot(1 - pexp(0:12, 15/24), type="b")
```

## Assignment 5

*At a tram stop, a tram passes every 10 minutes on average. There is no further information about the timetable in the city in question. How long do I have to wait for the tram on average from the moment I arrive at the tram stop?*

```{r}
(0.5)*(600)^2 / 600 / 60
```
Assuming the tram stops for 20 seconds:

```{r}
(0.5)*(600 - 20)^2 / 600 / 60
```

